The Small World Network Effect in Open Source Project Teams \author{Kevin Peterson\\ \small \texttt{pete1968@umn.edu} }

### 2013-11-13 paper/main.tex
Updated main.
Swapped in the freecode data.
Progress... added a few more images.

\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathrsfs}

@@

We calcluate the \textit{Clustering Coefficient} (or $CC$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
\[cc = 3 \times \frac{\text{number of triangles}}
                    {\text{number of connected triples}}\]

Also, measuring \textit{Path Length} ($PL$) allows us to gauge how far removed developers in the graph are from one another. For example

\subsection{Collection and Storage}

\subsection{Analysis}

@@

>>>>

\documentclass{proc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{fixltx2e}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{caption}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{tikz}

@@

\subsection{Collection and Storage}
Data was collected using the freely available FLOSSmole\cite{floss2006} data sets of free and open source projects. The data collection used was collected from the popular open source project site FreeCode\footnote{http://freecode.com/}, and contains data up to September, 2013.

\subsection{Analysis}
Results were analyzed using the Python graph processing packaged NetworkX\cite{hagberg-2008-exploring}.

We calcluate the \textit{Clustering Coefficient} (or $C^\delta$) as a measure of the proportion of closed triangles in a graph\cite{newman2003structure}:
\[C^\delta = 3 \times \frac{\text{number of triangles}}
                    {\text{number of connected triples}}\]

Also, measuring \textit{Path Length} ($L$) allows us to gauge how far removed developers in the graph are from one another. For example

\begin{tikzpicture}
  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
  \node (n1) at (15,8) {1};
  \node (n2) at (12,6)  {2};
  \node (n3) at (9,5)  {3};
  \node (n4) at (6,5)  {4};

  \draw ({n1}) -- ({n2});
  \draw ({n2}) -- ({n3});
  \draw ({n3}) -- ({n4});
\end{tikzpicture}

\begin{tikzpicture}
  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
  \node (n1) at (15,8) {1};
  \node (n2) at (12,5)  {2};
  \node (n3) at (9,5)  {3};
  \node (n4) at (11,8)  {4};

  \draw ({n1}) -- ({n2});
  \draw ({n2}) -- ({n3});
  \draw ({n3}) -- ({n4});
  \draw ({n1}) -- ({n4});
  \draw ({n1}) -- ({n3});
  \draw ({n2}) -- ({n4});
\end{tikzpicture}

\begin{tikzpicture}
  [scale=.5,auto=left,every node/.style={circle,fill=gray!20}]
  \node (n1) at (15,7) {1};
  \node (n2) at (12,5)  {2};
  \node (n3) at (8,7)  {3};
  \node (n4) at (11,8)  {4};

  \draw ({n1}) -- ({n2});
  \draw ({n3}) -- ({n4});
  \draw ({n1}) -- ({n4});
  \draw ({n2}) -- ({n4});
\end{tikzpicture}

\textit{Small-World-ness}

\[\gamma^{\Delta}_g = \frac{C^{\Delta}_g }{C^{\Delta}_{rand} } \]

\[\lambda_g = \frac{L_g }{L_{rand} } \]

\[S^\Delta = \frac{\gamma^{\Delta}_g }{\lambda_g} \]

@@

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-popular.png}
\end{center}

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-unpopular.png}
\end{center}

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-q-histo.png}
\end{center}

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-smallworld-histo.png}
\end{center}

\begin{center}
\includegraphics[width=0.5\textwidth]{images/freecode-graph.png}
\end{center}
